\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-12 paper.tex
added

\begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
    \centering
    \includegraphics[width=\textwidth]{vertex_subregions.jpeg}  % Adjust width as needed
    \caption{This illustration shows the process of DBRP and demonstrates a simple min-cut for a single subregion (D). The key challenge of the DBRP is finding a set of edge weights such that ALL possible min-cuts match ALL given boundary entropies simultaneously. For more complex combinations like S(ABC), S(ABD), etc., additional entropy constraints must be implemented to ensure the solution accurately represents the entanglement structure of the boundary theory.}  % Caption text
    \label{fig:single subregion min-cut}  % Label for referencing
\end{figure}
\newpage 
\section{Required Properties}
To ensure a solution exists we \textbf{need} the following properties:

\begin{enumerate}
    \item \textbf{Subadditivity (SA)}: entropy of \( A \) plus entropy of \( B \) is \( \geq \) entropy of \( A \cup B \)
    \[
    S(A) + S(B) \geq S(AB)
    \]
    \begin{center}
        \includegraphics[width=\linewidth]{subaddivity.png}
    \end{center}

>>>>

\begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
    \centering
    \includegraphics[width=\textwidth]{vertex_subregions.jpeg}  % Adjust width as needed
    \caption{This illustration shows the process of DBRP and demonstrates a simple min-cut for a single subregion (D). The key challenge of the DBRP is finding a set of edge weights such that ALL possible min-cuts match ALL given boundary entropies simultaneously. For more complex combinations like S(ABC), S(ABD), etc., additional entropy constraints must be implemented to ensure the solution accurately represents the entanglement structure of the boundary theory.}  % Caption text
    \label{fig:single subregion min-cut}  % Label for referencing
\end{figure}
\newpage 
\subsection{Entropy Constraints}
To ensure a solution exists where all possible min-cuts match all given boundary entropies. We \textbf{need} the following properties:

\begin{enumerate}
    \item \textbf{Subadditivity (SA)}: Entropy of combined system is at most the sum of information in the individual components.
    This property ensures redundancy exists when storing information across multiple locations. Meaning, potential information overlaps between components, which ensures recovery mechanisms.
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=\textwidth]{subadditivity.jpeg}  % Adjust width as needed
        \caption{The red line value has to be less than or equal to the sum of orange line values in order to ensure subadditivity.}  % Caption text
        \label{fig:Subadditivity}  % Label for referencing
    \end{figure}
